---
title: "Ports of animation examples — animint2 Gallery"
output:
  html_document:
    self_contained: true
    theme: null
    highlight: null
    mathjax: null
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
meta       <- tryCatch(read.csv("meta.csv",  stringsAsFactors = FALSE), error = function(e) data.frame())
error_meta <- tryCatch(read.csv("error.csv", stringsAsFactors = FALSE), error = function(e) data.frame())

# ── Helper: build card HTML ──────────────────────────────────────────────────
make_card <- function(owner_repo, title, viz_link, source_link, is_mine = FALSE) {
  local_png <- paste0("repos/", gsub("/", "_", owner_repo), ".png")
  raw_png   <- paste0("https://raw.githubusercontent.com/", owner_repo,
                      "/gh-pages/Capture.PNG")
  author    <- strsplit(owner_repo, "/")[[1]][1]

  if (is_mine) {
    card_class  <- "card mine"
    btn_class   <- "btn btn-mine"
    ribbon      <- '<span class="mine-ribbon">MINE</span>'
    author_line <- '<p class="card-author"><span class="you-badge">Nishita Shah</span></p>'
  } else {
    card_class  <- "card"
    btn_class   <- "btn btn-live"
    ribbon      <- ""
    author_line <- sprintf('<p class="card-author">%s</p>', author)
  }

  sprintf(
    '<div class="%s">
      <a href="%s" target="_blank" class="thumb-link">
        <div class="card-thumb">
          %s
          <img src="%s"
               onerror="this.src=\'%s\';this.onerror=function(){this.style.display=\'none\';this.parentNode.innerHTML+=\'<span class=no-img>No screenshot</span>\'}">
        </div>
      </a>
      <div class="card-body">
        <p class="card-title">%s</p>
        %s
        <div class="card-links">
          <a href="%s" class="%s" target="_blank">&#9654; Live</a>
          <a href="%s" class="btn btn-src" target="_blank">Source</a>
          <a href="https://github.com/%s" class="btn btn-repo" target="_blank">Repo</a>
        </div>
      </div>
    </div>',
    card_class,
    viz_link,
    ribbon,
    local_png, raw_png,
    title,
    author_line,
    viz_link, btn_class,
    source_link,
    owner_repo
  )
}
```

<style>
/* ── Base ── */
*, *::before, *::after { box-sizing: border-box; margin: 0; padding: 0; }
body {
  font-family: 'Inter', 'Segoe UI', system-ui, sans-serif;
  background: #f7f9fc;
  color: #1e2535;
}

/* ── Hero banner ── */
.hero {
  background: linear-gradient(120deg, #0f2544 0%, #1a5fa8 55%, #1a9e6e 100%);
  color: #fff;
  padding: 3.2rem 1.5rem 2.8rem;
  text-align: center;
}
.hero h1 { font-size: 2.2rem; font-weight: 800; letter-spacing: -0.5px; margin-bottom: 0.5rem; }
.hero .sub { font-size: 1rem; opacity: 0.85; margin-bottom: 1.6rem; }
.hero a { color: #7dd3fc; text-decoration: none; }
.hero a:hover { text-decoration: underline; }
.stat-row {
  display: inline-flex; gap: 0;
  background: rgba(255,255,255,0.12);
  border: 1px solid rgba(255,255,255,0.2);
  border-radius: 14px; overflow: hidden;
  backdrop-filter: blur(6px);
}
.stat-item {
  padding: 0.65rem 1.8rem;
  border-right: 1px solid rgba(255,255,255,0.15);
  text-align: center;
}
.stat-item:last-child { border-right: none; }
.stat-item .val { display: block; font-size: 1.5rem; font-weight: 700; line-height: 1.2; }
.stat-item .key { display: block; font-size: 0.65rem; opacity: 0.75; text-transform: uppercase; letter-spacing: 0.1em; margin-top: 2px; }

/* ── Page wrapper ── */
.wrap { max-width: 1180px; margin: 0 auto; padding: 2.5rem 1.4rem 4rem; }

/* ── Section heading ── */
.sec-head {
  display: flex; align-items: center; gap: 10px;
  margin: 2.4rem 0 1.2rem;
}
.sec-head .label {
  font-size: 0.72rem; font-weight: 700;
  text-transform: uppercase; letter-spacing: 0.13em;
  color: #8492a6; white-space: nowrap;
}
.sec-head .rule { flex: 1; height: 1px; background: #dde3ed; }
.pill {
  font-size: 0.68rem; font-weight: 600;
  padding: 3px 11px; border-radius: 99px;
  white-space: nowrap;
}
.pill-blue  { background: #e8f0fe; color: #1a56db; border: 1px solid #c3d6fb; }
.pill-green { background: #e6faf2; color: #166534; border: 1px solid #a7f3d0; }
.pill-red   { background: #fff1f1; color: #b91c1c; border: 1px solid #fca5a5; }

/* ── Card grid ── */
.grid {
  display: grid;
  grid-template-columns: repeat(auto-fill, minmax(270px, 1fr));
  gap: 1.2rem;
}

/* ── Card ── */
.card {
  background: #fff;
  border: 1px solid #e4e9f2;
  border-radius: 14px;
  overflow: hidden;
  display: flex; flex-direction: column;
  transition: transform 0.17s ease, box-shadow 0.17s ease, border-color 0.17s ease;
}
.card:hover {
  transform: translateY(-5px);
  box-shadow: 0 14px 32px rgba(15,37,68,0.10);
  border-color: #b6c8e8;
}
.card.mine {
  border: 2px solid #10b981;
  box-shadow: 0 0 0 4px rgba(16,185,129,0.08);
}

/* ── Thumbnail ── */
.thumb-link { display: block; text-decoration: none; }
.card-thumb {
  position: relative;
  width: 100%; height: 158px;
  background: linear-gradient(135deg, #e8f0fe 0%, #e6faf2 100%);
  overflow: hidden;
  display: flex; align-items: center; justify-content: center;
}
.card-thumb img {
  width: 100%; height: 100%; object-fit: cover;
  transition: transform 0.28s ease;
}
.card:hover .card-thumb img { transform: scale(1.06); }
.no-img { font-size: 0.72rem; color: #9aaabb; }
.mine-ribbon {
  position: absolute; top: 13px; right: -24px;
  background: #10b981; color: #fff;
  font-size: 0.6rem; font-weight: 700; letter-spacing: 0.1em;
  padding: 4px 30px; transform: rotate(35deg);
  pointer-events: none; z-index: 2;
}

/* ── Card body ── */
.card-body { padding: 14px 15px 15px; flex: 1; display: flex; flex-direction: column; }
.card-title {
  font-size: 0.92rem; font-weight: 600; color: #1e2535;
  line-height: 1.38; margin-bottom: 5px;
}
.card-author { font-size: 0.73rem; color: #7a8799; margin-bottom: 13px; }
.you-badge {
  display: inline-block;
  font-size: 0.68rem; font-weight: 600;
  padding: 2px 9px; border-radius: 99px;
  background: #e6faf2; color: #065f46;
  border: 1px solid #a7f3d0;
}
.card-links { display: flex; gap: 6px; flex-wrap: wrap; margin-top: auto; }

/* ── Buttons ── */
.btn {
  font-size: 0.7rem; font-weight: 600;
  padding: 4px 12px; border-radius: 99px;
  text-decoration: none; border: 1px solid transparent;
  transition: opacity 0.15s, background 0.15s;
  white-space: nowrap;
}
.btn:hover { opacity: 0.85; }
.btn-live  { background: #1a56db; color: #fff; border-color: #1a56db; }
.btn-mine  { background: #10b981; color: #fff; border-color: #10b981; }
.btn-src   { background: #f0f4ff; color: #1a56db; border-color: #c3d6fb; }
.btn-repo  { background: #f5f7fa; color: #4a5568; border-color: #dde3ed; }

/* ── Error cards ── */
.err-grid {
  display: grid;
  grid-template-columns: repeat(auto-fill, minmax(300px, 1fr));
  gap: 0.7rem;
}
.err-card {
  display: flex; align-items: flex-start; gap: 9px;
  background: #fff8f8; border: 1px solid #fca5a5;
  border-radius: 10px; padding: 10px 13px;
  font-size: 0.76rem; color: #7f1d1d; line-height: 1.45;
}
.err-icon { font-size: 1rem; flex-shrink: 0; margin-top: 1px; }
.err-card a { color: #b91c1c; font-weight: 600; text-decoration: none; }
.err-card a:hover { text-decoration: underline; }

/* ── Footer ── */
.footer {
  text-align: center; padding: 1.4rem 1rem;
  font-size: 0.76rem; color: #9aaabb;
  border-top: 1px solid #dde3ed; margin-top: 2.5rem;
}
.footer a { color: #4a90d9; text-decoration: none; }
.footer a:hover { text-decoration: underline; }
</style>

<!-- ═══════════ HERO ═══════════ -->
<div class="hero">
  <h1>Ports of animation examples</h1>
  <p class="sub">
    animint2 ports of the
    <a href="https://yihui.org/animation/examples/">animation package</a>
    &nbsp;—&nbsp; interactive statistical visualizations
    &nbsp;·&nbsp;
    <a href="https://github.com/tdhock/animint/wiki/Ports-of-animation-examples">wiki page</a>
  </p>
  <div class="stat-row">

```{r stats, echo=FALSE, results='asis'}
cat(sprintf(
  '<div class="stat-item"><span class="val">%d</span><span class="key">Visualizations</span></div>',
  nrow(meta)
))
cat('<div class="stat-item"><span class="val">animint2</span><span class="key">Package</span></div>')
cat('<div class="stat-item"><span class="val">GSoC 2026</span><span class="key">Program</span></div>')
```

  </div>
</div>

<!-- ═══════════ PAGE BODY ═══════════ -->
<div class="wrap">

<!-- ── YOUR CONTRIBUTION ── -->
<div class="sec-head">
  <span class="label">Your Contribution</span>
  <div class="rule"></div>
  <span class="pill pill-green">Nishita Shah</span>
</div>
<div class="grid">

```{r yours, echo=FALSE, results='asis'}
# Use viz_owner_repo column (actual column name from meta.csv)
if (nrow(meta) > 0 && "viz_owner_repo" %in% names(meta)) {
  yours  <- meta[grepl("Nishita-shah1", meta$viz_owner_repo, ignore.case = TRUE), ]
} else {
  yours <- data.frame()
}

if (nrow(yours) > 0) {
  for (i in seq_len(nrow(yours))) {
    r         <- yours[i, ]
    owner_repo <- r$viz_owner_repo
    viz_link   <- paste0("https://", strsplit(owner_repo, "/")[[1]][1],
                         ".github.io/", strsplit(owner_repo, "/")[[1]][2], "/")
    src_link   <- if ("source" %in% names(r)) r$source else "#"
    cat(make_card(owner_repo, r$title, viz_link, src_link, is_mine = TRUE))
  }
} else {
  cat('<p style="color:#8492a6;font-size:0.85rem;padding:0.4rem 0 1rem;">
        No contributions found — make sure your repo is listed in repos.txt.</p>')
}
```

</div>

<!-- ── ALL PORTS ── -->
<div class="sec-head">
  <span class="label">All Ports</span>
  <div class="rule"></div>

```{r all-badge, echo=FALSE, results='asis'}
if (nrow(meta) > 0 && "viz_owner_repo" %in% names(meta)) {
  others <- meta[!grepl("Nishita-shah1", meta$viz_owner_repo, ignore.case = TRUE), ]
} else {
  others <- data.frame()
}
cat(sprintf('<span class="pill pill-blue">%d ports</span>', nrow(others)))
```

</div>
<div class="grid">

```{r others, echo=FALSE, results='asis'}
if (nrow(others) > 0) {
  for (i in seq_len(nrow(others))) {
    r          <- others[i, ]
    owner_repo <- r$viz_owner_repo
    parts      <- strsplit(owner_repo, "/")[[1]]
    viz_link   <- paste0("https://", parts[1], ".github.io/", parts[2], "/")
    src_link   <- if ("source" %in% names(r)) r$source else "#"
    cat(make_card(owner_repo, r$title, viz_link, src_link, is_mine = FALSE))
  }
} else {
  cat('<p style="color:#8492a6;font-size:0.85rem;">No other ports found.</p>')
}
```

</div>

<!-- ── MISSING SCREENSHOTS ── -->

```{r errors, echo=FALSE, results='asis'}
if (nrow(error_meta) > 0) {
  cat(sprintf(
    '<div class="sec-head">
       <span class="label">Missing Screenshots</span>
       <div class="rule"></div>
       <span class="pill pill-red">%d repos</span>
     </div>
     <div class="err-grid">',
    nrow(error_meta)
  ))
  for (i in seq_len(nrow(error_meta))) {
    r          <- error_meta[i, ]
    owner_repo <- if ("viz_owner_repo" %in% names(r)) r$viz_owner_repo else r$viz.link
    parts      <- strsplit(owner_repo, "/")[[1]]
    viz_link   <- if (length(parts) >= 2) {
      paste0("https://", parts[1], ".github.io/", parts[2], "/")
    } else r$viz.link
    err_msg    <- if ("error" %in% names(r)) r$error else "unknown error"
    cat(sprintf(
      '<div class="err-card">
         <span class="err-icon">&#9888;</span>
         <div><a href="%s" target="_blank">%s</a><br>%s</div>
       </div>',
      viz_link, owner_repo, err_msg
    ))
  }
  cat('</div>')
}
```

</div><!-- end .wrap -->

<div class="footer">
  Built with
  <a href="https://github.com/animint/animint2" target="_blank">animint2</a>
  &nbsp;&middot;&nbsp;
  <a href="meta.csv">Download meta.csv</a>
  &nbsp;&middot;&nbsp;
  <a href="https://github.com/tdhock/animint/wiki/Ports-of-animation-examples" target="_blank">Wiki page</a>
</div>
