---
title: "Ports of animation examples — animint2 Gallery"
output:
  html_document:
    self_contained: true
    theme: null
    highlight: null
    mathjax: null
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
meta       <- tryCatch(read.csv("meta.csv",  stringsAsFactors = FALSE), error = function(e) data.frame())
error_meta <- tryCatch(read.csv("error.csv", stringsAsFactors = FALSE), error = function(e) data.frame())
```

<style>
* { box-sizing: border-box; margin: 0; padding: 0; }
body {
  font-family: 'Segoe UI', system-ui, -apple-system, sans-serif;
  background: #f0f4f8;
  color: #1a202c;
  min-height: 100vh;
}

/* Hero */
.hero {
  background: linear-gradient(135deg, #1a365d 0%, #2d6a9f 50%, #38a169 100%);
  color: white;
  text-align: center;
  padding: 3rem 2rem 2.5rem;
}
.hero h1 { font-size: 2.4rem; font-weight: 700; letter-spacing: -0.5px; margin-bottom: 0.6rem; }
.hero p  { font-size: 1.05rem; opacity: 0.88; margin-bottom: 1.4rem; }
.hero a  { color: #90cdf4; }
.hero-stats {
  display: inline-flex;
  gap: 2rem;
  background: rgba(255,255,255,0.15);
  border-radius: 12px;
  padding: 0.7rem 2rem;
  backdrop-filter: blur(4px);
}
.hero-stat { text-align: center; }
.hero-stat .num { font-size: 1.6rem; font-weight: 700; display: block; }
.hero-stat .lbl { font-size: 0.72rem; opacity: 0.8; text-transform: uppercase; letter-spacing: 0.06em; }

/* Layout */
.page-wrap { max-width: 1200px; margin: 0 auto; padding: 2.5rem 1.5rem 3rem; }

/* Section header */
.section-header { display: flex; align-items: center; gap: 10px; margin: 2rem 0 1.2rem; }
.section-header h2 { font-size: 0.78rem; font-weight: 700; text-transform: uppercase; letter-spacing: 0.12em; color: #718096; white-space: nowrap; }
.section-header .line { flex: 1; height: 1px; background: #e2e8f0; }
.section-header .badge { font-size: 0.7rem; padding: 2px 10px; border-radius: 20px; background: #ebf8ff; color: #2b6cb0; border: 1px solid #bee3f8; white-space: nowrap; }
.section-header .badge.mine { background: #f0fff4; color: #276749; border-color: #9ae6b4; }

/* Grid */
.grid { display: grid; grid-template-columns: repeat(auto-fill, minmax(280px, 1fr)); gap: 1.25rem; }

/* Card */
.card {
  background: white;
  border-radius: 14px;
  overflow: hidden;
  border: 1px solid #e2e8f0;
  transition: transform 0.18s ease, box-shadow 0.18s ease;
  display: flex;
  flex-direction: column;
}
.card:hover { transform: translateY(-4px); box-shadow: 0 12px 28px rgba(0,0,0,0.10); border-color: #cbd5e0; }
.card.mine  { border: 2px solid #38a169; box-shadow: 0 0 0 3px rgba(56,161,105,0.10); }

/* Thumbnail */
.card-thumb {
  width: 100%; height: 155px;
  background: linear-gradient(135deg, #ebf4ff, #e6fffa);
  display: flex; align-items: center; justify-content: center;
  overflow: hidden; position: relative;
}
.card-thumb img { width: 100%; height: 100%; object-fit: cover; transition: transform 0.3s ease; }
.card:hover .card-thumb img { transform: scale(1.04); }
.no-img { font-size: 0.75rem; color: #a0aec0; text-align: center; padding: 1rem; }
.mine-ribbon {
  position: absolute; top: 10px; right: -22px;
  background: #38a169; color: white;
  font-size: 0.65rem; font-weight: 700; letter-spacing: 0.08em;
  padding: 3px 28px; transform: rotate(35deg); text-transform: uppercase;
  pointer-events: none;
}

/* Card body */
.card-body { padding: 14px 16px 16px; flex: 1; display: flex; flex-direction: column; }
.card-title { font-size: 0.95rem; font-weight: 600; color: #2d3748; margin-bottom: 4px; line-height: 1.35; }
.card-author { font-size: 0.75rem; color: #718096; margin-bottom: 12px; }
.card-links { display: flex; gap: 6px; flex-wrap: wrap; margin-top: auto; }
.card-link {
  font-size: 0.72rem; font-weight: 500; padding: 4px 11px;
  border-radius: 20px; text-decoration: none;
  border: 1px solid #e2e8f0; color: #2b6cb0; background: #ebf8ff;
  transition: background 0.15s;
}
.card-link:hover { background: #bee3f8; }
.card-link.demo  { background: #2b6cb0; color: white; border-color: #2b6cb0; }
.card-link.demo:hover { background: #2c5282; }
.card-link.mine-demo  { background: #38a169; color: white; border-color: #38a169; }
.card-link.mine-demo:hover { background: #276749; }

/* Error section */
.error-grid { display: grid; grid-template-columns: repeat(auto-fill, minmax(320px, 1fr)); gap: 0.75rem; }
.error-card {
  background: #fff5f5; border: 1px solid #fed7d7; border-radius: 10px;
  padding: 10px 14px; font-size: 0.78rem; color: #744210;
  display: flex; align-items: flex-start; gap: 8px;
}
.error-card::before { content: "⚠"; font-size: 1rem; color: #e53e3e; flex-shrink: 0; }
.error-card a { color: #c05621; font-weight: 500; }

/* Footer */
.gallery-footer {
  text-align: center; padding: 1.5rem;
  font-size: 0.78rem; color: #a0aec0;
  border-top: 1px solid #e2e8f0; margin-top: 2rem;
}
.gallery-footer a { color: #4a90d9; text-decoration: none; }
</style>

<!-- HERO -->
<div class="hero">
  <h1>Ports of animation examples</h1>
  <p>
    animint2 ports of the
    <a href="https://yihui.org/animation/examples/">animation package</a>
    — interactive statistical visualizations &nbsp;·&nbsp;
    <a href="https://github.com/tdhock/animint/wiki/Ports-of-animation-examples">wiki page</a>
  </p>
  <div class="hero-stats">

```{r hero-stats, echo=FALSE, results='asis'}
cat(sprintf(
  '<div class="hero-stat"><span class="num">%d</span><span class="lbl">Visualizations</span></div>',
  nrow(meta)
))
cat('<div class="hero-stat"><span class="num">animint2</span><span class="lbl">Package</span></div>')
cat('<div class="hero-stat"><span class="num">GSoC</span><span class="lbl">2026</span></div>')
```

  </div>
</div>

<div class="page-wrap">

<!-- ── YOUR CONTRIBUTION ── -->
<div class="section-header">
  <h2>Your Contribution</h2>
  <div class="line"></div>
  <span class="badge mine">Nishita Shah</span>
</div>
<div class="grid">

```{r yours-cards, echo=FALSE, results='asis'}
yours <- if (nrow(meta) > 0) {
  meta[grepl("Nishita-shah1", meta$repo.link, ignore.case = TRUE), ]
} else data.frame()

if (nrow(yours) > 0) {
  for (i in seq_len(nrow(yours))) {
    r <- yours[i, ]
    owner_repo <- sub("https://github.com/", "", r$repo.link)
    owner_repo <- sub("/tree/gh-pages.*", "", owner_repo)
    local_png  <- paste0("repos/", gsub("/", "_", owner_repo), ".png")
    raw_png    <- paste0("https://raw.githubusercontent.com/", owner_repo, "/gh-pages/Capture.PNG")
    cat(sprintf(
      '<div class="card mine">
        <div class="card-thumb">
          <span class="mine-ribbon">yours</span>
          <img src="%s"
               onerror="this.src=\'%s\';this.onerror=function(){this.style.display=\'none\';this.parentNode.innerHTML+=\'<div class=no-img>No screenshot yet</div>\'}">
        </div>
        <div class="card-body">
          <p class="card-title">%s</p>
          <p class="card-author">Nishita Shah</p>
          <div class="card-links">
            <a href="%s" class="card-link mine-demo" target="_blank">&#9654; Live Demo</a>
            <a href="%s" class="card-link" target="_blank">Source</a>
            <a href="%s" class="card-link" target="_blank">Repo</a>
          </div>
        </div>
      </div>',
      local_png, raw_png,
      r$title,
      r$viz.link, r$source.link, r$repo.link
    ))
  }
} else {
  cat('<p style="color:#718096;font-size:0.85rem;padding:0.5rem 0;">No contributions found for Nishita-shah1.</p>')
}
```

</div>

<!-- ── ALL PORTS ── -->
<div class="section-header">
  <h2>All Ports</h2>
  <div class="line"></div>

```{r all-badge, echo=FALSE, results='asis'}
others <- if (nrow(meta) > 0) {
  meta[!grepl("Nishita-shah1", meta$repo.link, ignore.case = TRUE), ]
} else data.frame()
cat(sprintf('<span class="badge">%d ports</span>', nrow(others)))
```

</div>
<div class="grid">

```{r others-cards, echo=FALSE, results='asis'}
if (nrow(others) > 0) {
  for (i in seq_len(nrow(others))) {
    r <- others[i, ]
    owner_repo <- sub("https://github.com/", "", r$repo.link)
    owner_repo <- sub("/tree/gh-pages.*", "", owner_repo)
    local_png  <- paste0("repos/", gsub("/", "_", owner_repo), ".png")
    raw_png    <- paste0("https://raw.githubusercontent.com/", owner_repo, "/gh-pages/Capture.PNG")
    author     <- strsplit(owner_repo, "/")[[1]][1]
    cat(sprintf(
      '<div class="card">
        <div class="card-thumb">
          <img src="%s"
               onerror="this.src=\'%s\';this.onerror=function(){this.style.display=\'none\';this.parentNode.innerHTML+=\'<div class=no-img>No screenshot</div>\'}">
        </div>
        <div class="card-body">
          <p class="card-title">%s</p>
          <p class="card-author">%s</p>
          <div class="card-links">
            <a href="%s" class="card-link demo" target="_blank">&#9654; Live</a>
            <a href="%s" class="card-link" target="_blank">Source</a>
            <a href="%s" class="card-link" target="_blank">Repo</a>
          </div>
        </div>
      </div>',
      local_png, raw_png,
      r$title, author,
      r$viz.link, r$source.link, r$repo.link
    ))
  }
} else {
  cat('<p style="color:#718096;font-size:0.85rem;">No other ports found.</p>')
}
```

</div>

<!-- ── MISSING METADATA ── -->

```{r errors-section, echo=FALSE, results='asis'}
if (nrow(error_meta) > 0) {
  cat(sprintf(
    '<div class="section-header">
      <h2>Missing Screenshots</h2>
      <div class="line"></div>
      <span class="badge" style="background:#fff5f5;color:#c05621;border-color:#feb2b2;">%d repos</span>
    </div>
    <div class="error-grid">',
    nrow(error_meta)
  ))
  for (i in seq_len(nrow(error_meta))) {
    r <- error_meta[i, ]
    cat(sprintf(
      '<div class="error-card"><a href="%s" target="_blank">%s</a> — %s</div>',
      r$viz.link, r$viz_owner_repo, r$error
    ))
  }
  cat('</div>')
}
```

</div><!-- end page-wrap -->

<div class="gallery-footer">
  Built with <a href="https://github.com/animint/animint2" target="_blank">animint2</a> &nbsp;&middot;&nbsp;
  <a href="meta.csv">Download meta.csv</a> &nbsp;&middot;&nbsp;
  <a href="https://github.com/tdhock/animint/wiki/Ports-of-animation-examples" target="_blank">Wiki page</a>
</div>
