---
title: "Ports of animation examples — animint2 Gallery"
output: html_document
---

<style>
body { font-family: sans-serif; max-width: 1100px; margin: 0 auto; padding: 2rem; }
.gallery-header { border-bottom: 1px solid #eee; padding-bottom: 1.5rem; margin-bottom: 2rem; }
.gallery-header h1 { font-size: 24px; font-weight: 500; margin: 0 0 6px; }
.gallery-header p { font-size: 14px; color: #666; margin: 0 0 10px; }
.tags { display: flex; gap: 8px; flex-wrap: wrap; }
.tag { font-size: 11px; padding: 3px 10px; border-radius: 20px; border: 1px solid #ddd; color: #666; }
.section-label { font-size: 11px; font-weight: 500; color: #999; letter-spacing: 0.08em; text-transform: uppercase; margin: 0 0 12px; }
.grid { display: grid; grid-template-columns: repeat(auto-fill, minmax(240px, 1fr)); gap: 16px; margin-bottom: 2rem; }
.card { background: #fff; border: 1px solid #eee; border-radius: 12px; overflow: hidden; }
.card:hover { border-color: #ccc; }
.card-thumb { width: 100%; height: 130px; background: #f5f5f5; display: flex; align-items: center; justify-content: center; border-bottom: 1px solid #eee; overflow: hidden; }
.card-thumb img { width: 100%; height: 100%; object-fit: cover; }
.card-thumb-label { font-size: 11px; color: #bbb; }
.card-body { padding: 12px 14px; }
.card-title { font-size: 13px; font-weight: 500; color: #111; margin: 0 0 4px; }
.card-author { font-size: 12px; color: #888; margin: 0 0 10px; }
.card-links { display: flex; gap: 6px; flex-wrap: wrap; }
.card-link { font-size: 11px; padding: 3px 10px; border-radius: 20px; border: 1px solid #ddd; color: #185FA5; text-decoration: none; }
.card-link:hover { background: #f0f0f0; }
.yours { border: 2px solid #1D9E75; }
.yours .card-thumb { background: #E1F5EE; }
.yours-badge { font-size: 10px; padding: 2px 8px; border-radius: 20px; background: #E1F5EE; color: #0F6E56; margin-left: 6px; }
.error-section { margin-top: 2rem; border-top: 1px solid #eee; padding-top: 1.5rem; }
.error-card { background: #fff8f8; border: 1px solid #fdd; border-radius: 8px; padding: 10px 14px; margin-bottom: 8px; font-size: 12px; color: #666; }
</style>

```{r echo=FALSE, message=FALSE, warning=FALSE}
meta       <- tryCatch(read.csv("meta.csv",  stringsAsFactors = FALSE), error = function(e) data.frame())
error_meta <- tryCatch(read.csv("error.csv", stringsAsFactors = FALSE), error = function(e) data.frame())
```

<div class="gallery-header">
<h1>Ports of animation examples</h1>
<p>animint2 ports of the <a href="https://yihui.org/animation/examples/">animation package</a> — interactive statistical visualizations. Original list: <a href="https://github.com/tdhock/animint/wiki/Ports-of-animation-examples">wiki page</a></p>
<div class="tags">

```{r echo=FALSE, results='asis'}
cat(sprintf('<span class="tag">%d visualizations</span>', nrow(meta)))
cat('<span class="tag">animint2</span>')
cat('<span class="tag">GSoC 2026</span>')
```

</div>
</div>

<p class="section-label">your contribution</p>
<div class="grid">

```{r echo=FALSE, results='asis'}
yours <- meta[grepl("Nishita-shah1", meta$repo.link, ignore.case = TRUE), ]
if (nrow(yours) > 0) {
  for (i in seq_len(nrow(yours))) {
    r <- yours[i, ]
    png_url <- gsub("/tree/gh-pages", "/raw/gh-pages/Capture.PNG", r$repo.link)
    cat(sprintf(
      '<div class="card yours">
        <div class="card-thumb">
          <img src="%s" onerror="this.style.display=\'none\'">
        </div>
        <div class="card-body">
          <p class="card-title">%s <span class="yours-badge">yours</span></p>
          <p class="card-author">Nishita Shah</p>
          <div class="card-links">
            <a href="%s" class="card-link">demo</a>
            <a href="%s" class="card-link">source</a>
            <a href="%s" class="card-link">repo</a>
          </div>
        </div>
      </div>',
      png_url, r$title, r$viz.link, r$source.link, r$repo.link
    ))
  }
}
```

</div>

<p class="section-label">all ports</p>
<div class="grid">

```{r echo=FALSE, results='asis'}
others <- meta[!grepl("Nishita-shah1", meta$repo.link, ignore.case = TRUE), ]
if (nrow(others) > 0) {
  for (i in seq_len(nrow(others))) {
    r <- others[i, ]
    png_url <- gsub("/tree/gh-pages", "/raw/gh-pages/Capture.PNG", r$repo.link)
    cat(sprintf(
      '<div class="card">
        <div class="card-thumb">
          <img src="%s" onerror="this.parentNode.innerHTML=\'<span class=card-thumb-label>no screenshot</span>\'">
        </div>
        <div class="card-body">
          <p class="card-title">%s</p>
          <div class="card-links">
            <a href="%s" class="card-link">demo</a>
            <a href="%s" class="card-link">source</a>
            <a href="%s" class="card-link">repo</a>
          </div>
        </div>
      </div>',
      png_url, r$title, r$viz.link, r$source.link, r$repo.link
    ))
  }
}
```

</div>

```{r echo=FALSE, results='asis'}
if (nrow(error_meta) > 0) {
  cat('<div class="error-section">')
  cat('<p class="section-label">missing metadata</p>')
  for (i in seq_len(nrow(error_meta))) {
    r <- error_meta[i, ]
    cat(sprintf(
      '<div class="error-card"><a href="%s">%s</a> — %s</div>',
      r$viz.link, r$viz.link, r$error
    ))
  }
  cat('</div>')
}
```
